Syntax and Semantics of Abstract Binding Trees

### 2015-11-24 paper.tex
Define the least support

\newcommand\SymSets{\mathbb{I}}
\newcommand\FinSets{\mathbb{F}}
\newcommand\HypCat{\mathbf{H}}

@@

\begin{definition}[Support]
  For a presheaf $\Of{X}{\Sets^\SCtx}$, when
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r, hook, "\IMode{\varrho}"] & \IMode{\Upsilon'}
  \end{tikzcd},
  we say that $\Upsilon$ supports $\Member{m}{\Upsilon'}$ when, for all
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon'}\arrow[r, hook, "\IMode{\varrho_1}{,} \IMode{\varrho_2}"] & \IMode{\Upsilon''}
  \end{tikzcd},
  if $\IsEq{\varrho_1\circ\varrho}{\varrho_2\circ\varrho}$ then $\IsEq{m\varrho_1}{m\varrho_2}$.
\end{definition}

@@

@@

Abts are identified up to $\alpha$-equivalence. Let $\FS{M}$ be the collection
of symbols free in $M$, and let $\FV{M}$ be the collection of variables free in
$M$. \todo[inline]{actually define these}

@@

The only place that symbols appear in our calculus is as parameters to operators
(unlike variables, symbols are not terms). Therefore, the functorial action of
the operator presheaf can be lifted into terms by recursion on their
structure, via a pair of judgments $\IsRenaming{\varrho}{M}{N}$ and
$\IsRenaming{\varrho}{E}{F}$, presupposing $\Of{\varrho}{\Upsilon\inj\Upsilon'}$,
and $\IsAbt{\Theta}{\Upsilon}{\Gamma}{M}{\tau}$ and
$\IsAbt{\Theta}{\Upsilon}{\Gamma}{E}{v}$ respectively:

>>>>

\newcommand\SymSets{\mathbb{I}}
\newcommand\FinSets{\mathbb{F}}
\newcommand\HypCat{\mathbf{H}}
\newcommand\Supp[1]{\mathbf{supp}(#1)}
\newcommand\SupportsUnmoded[3]{#1 \blacktriangleright_{#2} #3}
\newcommand\Supports[3]{\SupportsUnmoded{\IMode{#1}}{\IMode{#2}}{\IMode{#3}}}

@@

\begin{definition}[Support]
  For a presheaf $\Of{X}{\Sets^\SCtx}$, when
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon}\arrow[r, hook, "\IMode{\varrho}"] & \IMode{\Upsilon'}
  \end{tikzcd},
  we say that $\Upsilon$ supports $\Member{m}{\Upsilon'}$ (written
  $\Supports{\Upsilon}{\varrho}{m}$) when, for all
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon'}\arrow[r, hook, "\IMode{\varrho_1}{,} \IMode{\varrho_2}"] & \IMode{\Upsilon''}
  \end{tikzcd},
  if $\IsEq{\varrho_1\circ\varrho}{\varrho_2\circ\varrho}$ then $\IsEq{m\varrho_1}{m\varrho_2}$.
\end{definition}

@@

Let $\Supp{m}$ be the \emph{least support} of $\Member{m}{X(\Upsilon')}$:
\[
  \Define{\Supp{m}}{
    \bigcap_{
      \begin{tikzcd}[cramped, ampersand replacement = \&]
        \Upsilon\arrow[r, hook, "\varrho"] \& \Upsilon'
      \end{tikzcd}
    }
    \SupportsUnmoded{\Upsilon}{\varrho}{m}
  }
\]
Intuitively, $\Supp{m}$ is the exact symbol context that $m$ depends on.

@@

Abts are identified up to $\alpha$-equivalence. Let $\FV{M}$ be the collection
of variables free in $M$, which is easily calculated by recursion on the
structure of $M$. We also intend to calculate the collection $\FS{M}$ of
symbols free in $M$, but this is more involved.

@@

The only place that symbols appear in our calculus is as parameters to operators
(unlike variables, symbols are not terms). Therefore, the functorial action of
the operator sheaf can be lifted into terms by recursion on their
structure, via a pair of judgments $\IsRenaming{\varrho}{M}{N}$ and
$\IsRenaming{\varrho}{E}{F}$, presupposing $\Of{\varrho}{\Upsilon\inj\Upsilon'}$,
and $\IsAbt{\Theta}{\Upsilon}{\Gamma}{M}{\tau}$ and
$\IsAbt{\Theta}{\Upsilon}{\Gamma}{E}{v}$ respectively:
